Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-17 prob.tex
prob.tex Updates here and there...

\begin{definition}[Probability Measure]\label{def:ClassicalProbabilitySpace}
Given the set of events $\events$, a \emph{probability measure} is
a function $\pmeas:\events\rightarrow[0,1]$ such that: 
\begin{itemize}
\item $\pmeas(\emptyset)=0$. 
\item $\pmeas(\Omega)=1$. 
\item for any event $E$, 
\begin{equation}
\pmeas\left(\Omega\backslash E\right)=1\tensor*[_{\mathbb{R}}]{-}{}\pmeas\left(E\right)\textrm{ ,}\label{eq:ClassicalReal-valuedProbability-Complement}
\end{equation}
where $\Omega\backslash E$ is the complement event, and $1\tensor*[_{\mathbb{R}}]{-}{}\pmeas\left(E\right)$
explicitly specifies $1$ and $\pmeas\left(E\right)\in\mathbb{R}$.
Besides $\mathbb{R}$, we will prepose other symbols later to specify
the type of operations, and they may be dropped when there is no ambiguity. 
\item for a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
events, $\pmeas(\bigcup_{i=1}^{N}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$.
Similar to the above condition, $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$
explicitly specifies $\pmeas(E_{i})\in\mathbb{R}$. 
\end{itemize}
\qed\end{definition}

@@

As motivated above, an event $E_{1}$ may have an interval of probability
$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
interval probability $[l_{2},r_{2}]$, what is the interval probability
of the event $E_{1}\cup E_{2}$? The answer is somewhat subtle: although
it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
as the combined probability, one can do find a much tighter interval
if information \emph{against} the event (i.e., information about the
complement event) is also taken into consideration. Formally, for
a general event $E$ with probability $[l,r]$, the evidence that
contradicts $E$ is an evidence supporting the complement of $E$.
The complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
which we abbreviate $\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
where the preposing $\mathscr{I}$ specifies we subtract intervals.
Given a collection of intervals $\mathscr{I}$, an $\mathscr{I}$\textendash interval-valued
probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
such that~\cite{JamisonLodwick2004}:\footnote{The right-end of the interval-valued probability measure is a special
case of (sub-additive) capacity~\cite{Choquet1954,Graf1980,Goodman2013}
or outer measure~\cite{Folland2013}. The left-end of the interval-valued
probability measure is a special case of game~\cite{Shapley1965}.} 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$, 
\item $\bar{\mu}(\Omega)=[1,1]$, 
\item for every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N'}\subseteq\events$
with $\Omega=\left(\bigcup_{i=1}^{N}E_{i}\right)\bigcup\left(\bigcup_{i=1}^{N'}E_{i}'\right)$,
we have 
\[
\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum r_{i}\right\} \right]\textrm{ ,}
\]
where $\bar{\mu}\left(E_{i}\right)=[l_{i},r_{i}]$ and $\bar{\mu}\left(E_{i}'\right)=[l_{i}',r_{i}']$
for all $i$.
\end{itemize}
In order to understand this definition, we tear the last condition
apart and provide an equivalent definition of interval-valued probability
measures.

\begin{lemma}\label{lem:classicalProbabilityMeasure}Given a sample
space~$\Omega$ and its event~$\events$, a function~$\bar{\mu}:\events\rightarrow[0,1]$
is a classical interval-valued probability measure if and only if
$\bar{\mu}$ satisfies the following conditions: 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$, 
\item $\bar{\mu}(\Omega)=[1,1]$, 
\item for any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$,
and 
\item for a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\bar{\mu}\left(E_{i}\right)$,
where $\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}r_{i}\right]$.
We may drop the preposing $\mathscr{I}$ when summands are clearly
intervals. 
\end{itemize}
\qed\end{lemma}

@@

For the general interval-valued probability measures, the following
theorem gives an algorithmic way to decide whether it has a non-empty
core.

\begin{thm}[Bondareva-Shapley~\cite{Shapley1967,Bondareva1968,Grabisch2016}]\label{thm:Bondareva-Shapley}
Let $l$ be the left-end of an interval-valued probability measure~$\bar{\mu}$,
$\bar{\mu}$ has a non-empty core if and only if for any minimal balanced
set~$\left\{ E_{i}\right\} _{i=1}^{N}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\gamma_{i}l\left(E_{i}\right)\le1$,
where $\left\{ E_{i}\right\} _{i=1}^{N}$ is called minimal balanced
set if they are distinct, $\emptyset\ne E_{i}\subsetneq\Omega$, and
there exist a unique positive coefficient~$\left\{ \gamma_{i}\right\} _{i=1}^{N}$
such that $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1\textrm{ and }\omega\in E_{i}}^{N}}\gamma_{i}=1$
for all $\omega\in\Omega$.

\qed\end{thm}

The Bondareva-Shapley theorem can be used to algorithmically decide
non-empty core because the minimal balanced set can be generated by
an algorithm~\cite{Peleg1965}. However, the number of minimal balanced
sets grows very rapidly with the size of $\Omega$, $\left|\Omega\right|$,
so that we have only verified every interval-valued probability measure
has a non-empty core when $\left|\Omega\right|\le5$ so far.

@@

\begin{definition}[Ideal Measurement; Complement; Commutativity]~ 
\begin{itemize}
\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is called
an \emph{ideal measurement} if it is a partition of the identity,
i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
be mutually orthogonal~\cite{Griffiths2003}.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal
to $P$, and corresponds to the complement event~$\Omega\backslash E$
in classical probability~\cite{Griffiths2003}. 
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical
intersection between events~\cite{peres1995quantum,Griffiths2003}. 
\item For two commuting projection operators $P_{1}$ and $P_{2}$, their
\emph{disjunction}~$P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}$
is defined to be $P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\tensor*[_{\mathscr{O}}]{-}{}P_{1}P_{2}$~\cite{Griffiths2003}. 
\end{itemize}
\qed\end{definition}

@@

\begin{definition}[Quantum Probability Measure~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
Given a Hilbert space $\Hilb$ with its set of events~$\events$,
a \emph{quantum probability measure} is a function~$\mu:\events\rightarrow[0,1]$
such that:\footnote{It is possible to define a more general space of events consisting
of all operators~$\mathcal{A}$ on $\Hilb$ and to extend $\mu$
linearly to $\mathcal{A}$ and consider $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
When an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$
is the expectation value of $A$ which could bigger than one because
$\mu$ is linear. We does not take this approach because we want to
focus only on probability. } 
\begin{itemize}
\item $\mu(\mathbb{0})=0$. 
\item $\mu(\mathbb{1})=1$. 
\item For any projection $P$, 
\begin{equation}
\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)\textrm{ .}\label{eq:QuantumReal-valuedProbability-Complement}
\end{equation}
\item for a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$. 
\end{itemize}
\qed\end{definition}

@@

Mathematically, given a Hilbert space~$\Hilb$ of dimension~$d$,
we can pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
and fix a density matrix~$\rho$ representing in the same basis,
i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
Applying the canonical inner product, we can define a Radon-Nikodym
derivative~$f_{\rho}:\Omega\rightarrow[0,1]$ by
\begin{equation}
f_{\rho}\left(\ket{\psi_{j}}\right)=\ip{\psi_{j}}{\rho\psi_{j}}=r_{jj}\textrm{ .}\label{eq:quantum-Radon-Nikodym}
\end{equation}
Furthermore, we only consider the quantum events~$\events'$ with
the form $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$,
where $E\in2^{\Omega}$. The classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
induced by the Radon-Nikodym derivative~$f_{\rho}$ is exactly the
Born rule of the mixed state~$\rho$~\cite{Maassen2010}, 
\begin{equation}
\pmeas'\left(E\right)\overset{\left(\ref{eq:Radon-Nikodym}\right)}{=}\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum f_{\rho}\left(\ket{\psi_{j}}\right)\overset{\left(\ref{eq:quantum-Radon-Nikodym}\right)}{=}\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}=\Tr\left(\rho P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\mu_{\rho}^{B}\left(P\right)\textrm{ .}\label{BornRule.mixed-1}
\end{equation}

In this sense, the Radon-Nikodym derivative~$f_{\rho}$ is a special
case of the mixed state~$\rho$, and the Radon-Nikodym theorem is
a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.

>>>>

\begin{definition}[Probability Measure]\label{def:ClassicalProbabilitySpace}
Given the set of events $\events$, a \emph{probability measure} is
a function $\pmeas:\events\rightarrow[0,1]$ such that: 
\begin{itemize}
\item $\pmeas(\emptyset)=0$. 
\item $\pmeas(\Omega)=1$. 
\item For any event $E$, 
\begin{equation}
\pmeas\left(\Omega\backslash E\right)=1\tensor*[_{\mathbb{R}}]{-}{}\pmeas\left(E\right)\textrm{ ,}\label{eq:ClassicalReal-valuedProbability-Complement}
\end{equation}
where $\Omega\backslash E$ is the complement event, and $1\tensor*[_{\mathbb{R}}]{-}{}\pmeas\left(E\right)$
explicitly specifies $1$ and $\pmeas\left(E\right)\in\mathbb{R}$.
Besides $\mathbb{R}$, we will prepose other symbols later to specify
the type of operations, and they may be dropped when there is no ambiguity. 
\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
events, $\pmeas(\bigcup_{i=1}^{N}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$.
Similar to the above condition, $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\pmeas(E_{i})$
explicitly specifies $\pmeas(E_{i})\in\mathbb{R}$. 
\end{itemize}
\qed\end{definition}

@@

As motivated above, an event $E_{1}$ may have an interval of probability
$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
interval probability $[l_{2},r_{2}]$, what is the interval probability
of the event $E_{1}\cup E_{2}$? The answer is somewhat subtle: although
it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
as the combined probability, one can do find a much tighter interval
if information \emph{against} the event (i.e., information about the
complement event) is also taken into consideration. Formally, for
a general event $E$ with probability $[l,r]$, the evidence that
contradicts $E$ is an evidence supporting the complement of $E$.
The complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
which we abbreviate $\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
where the preposing $\mathscr{I}$ specifies we subtract intervals.
Given a collection of intervals $\mathscr{I}$, an $\mathscr{I}$\textendash interval-valued
probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
such that~\cite{JamisonLodwick2004}:\footnote{The right-end of the interval-valued probability measure is a special
case of (sub-additive) capacity~\cite{Choquet1954,Graf1980,Goodman2013}
or outer measure~\cite{Folland2013}. The left-end of the interval-valued
probability measure is a special case of game~\cite{Shapley1965}.} 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$. 
\item $\bar{\mu}(\Omega)=[1,1]$. 
\item For every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N'}\subseteq\events$
with $\Omega=\left(\bigcup_{i=1}^{N}E_{i}\right)\bigcup\left(\bigcup_{i=1}^{N'}E_{i}'\right)$,
we have 
\[
\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum r_{i}\right\} \right]\textrm{ ,}
\]
where $\bar{\mu}\left(E_{i}\right)=[l_{i},r_{i}]$ and $\bar{\mu}\left(E_{i}'\right)=[l_{i}',r_{i}']$
for all $i$.
\end{itemize}
In order to understand this definition, we tear the last condition
apart and provide an equivalent definition of interval-valued probability
measures.

\begin{lemma}\label{lem:classicalProbabilityMeasure}Given a sample
space~$\Omega$ and its event~$\events$, a function~$\bar{\mu}:\events\rightarrow[0,1]$
is a classical interval-valued probability measure if and only if
$\bar{\mu}$ satisfies the following conditions: 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$.
\item $\bar{\mu}(\Omega)=[1,1]$. 
\item For any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$.
\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\bar{\mu}\left(E_{i}\right)$,
where $\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}r_{i}\right]$.
We may drop the preposing $\mathscr{I}$ when summands are clearly
intervals. 
\end{itemize}
\qed\end{lemma}

@@

For general interval-valued probability measures, the following theorem
gives an algorithmic way to decide whether it has a non-empty core.

\begin{thm}[Bondareva-Shapley~\cite{Shapley1967,Bondareva1968,Grabisch2016}]\label{thm:Bondareva-Shapley}
Let $l$ be the left-end of an interval-valued probability measure~$\bar{\mu}$,
$\bar{\mu}$ has a non-empty core if and only if for any minimal balanced
sets~$\left\{ E_{i}\right\} _{i=1}^{N}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\gamma_{i}l\left(E_{i}\right)\le1$,
where $\left\{ E_{i}\right\} _{i=1}^{N}$ is called minimal balanced
sets if they are distinct, $\emptyset\ne E_{i}\subsetneq\Omega$,
and there exist a unique positive coefficient~$\left\{ \gamma_{i}\right\} _{i=1}^{N}$
such that $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1\textrm{ and }\omega\in E_{i}}^{N}}\gamma_{i}=1$
for all $\omega\in\Omega$.\qed\end{thm}

The Bondareva-Shapley theorem can be used to algorithmically decide
non-empty core because the minimal balanced sets can be generated
by an algorithm~\cite{Peleg1965}. However, the number of minimal
balanced sets grows very rapidly with $\left|\Omega\right|$, the
size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially?}},
so that we have only verified every interval-valued probability measure
has a non-empty core when $\left|\Omega\right|\le5$ so far.

@@

\begin{definition}[Ideal Measurement; Complement; Commutativity;
disjunction]~ 
\begin{itemize}
\item A set of projections $\left\{ P_{i}\right\} _{i=1}^{N}$ is called
an \emph{ideal measurement} if it is a partition of the identity,
i.e., $\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}=\mathbb{1}$~\cite{Swart2013}.
In this case, projections $\left\{ P_{i}\right\} _{i=1}^{N}$ must
be mutually orthogonal~\cite{Griffiths2003}.
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called \emph{complement}. It is orthogonal
to $P$, and corresponds to the complement event~$\Omega\backslash E$
in classical probability~\cite{Griffiths2003}. 
\item Projection operators $P_{1}$ and $P_{2}$ \emph{commute} if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical
intersection between events~\cite{peres1995quantum,Griffiths2003}. 
\item For two commuting projection operators $P_{1}$ and $P_{2}$, their
\emph{disjunction}~$P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}$
is defined to be $P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\tensor*[_{\mathscr{O}}]{-}{}P_{1}P_{2}$~\cite{Griffiths2003}. 
\end{itemize}
\qed\end{definition}

@@

\begin{definition}[Quantum Probability Measure~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
Given a Hilbert space $\Hilb$ with its set of events~$\events$,
a \emph{quantum probability measure} is a function~$\mu:\events\rightarrow[0,1]$
such that:\footnote{It is possible to define a more general space of events consisting
of all operators~$\mathcal{A}$ on $\Hilb$ and to extend $\mu$
linearly to $\mathcal{A}$ and consider $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
When an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$
is the expectation value of $A$ which could bigger than one because
$\mu$ is linear. We does not take this approach because we want to
focus only on probability. } 
\begin{itemize}
\item $\mu(\mathbb{0})=0$. 
\item $\mu(\mathbb{1})=1$. 
\item For any projection $P$, 
\begin{equation}
\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)\textrm{ .}\label{eq:QuantumReal-valuedProbability-Complement}
\end{equation}
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{N}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\mu\left(P_{i}\right)$
. 
\end{itemize}
\qed\end{definition}

@@

Mathematically, to fix the magnetic field of the Stern-Gerlach experiment
is to pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
for a given Hilbert space~$\Hilb$ of dimension~$d$. If the state
of the silver atom is represented by a density matrix~$\rho$ written
in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=1}^{d}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{d}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
As we discussed in the last paragraph, the Born rule of the mixed
state~$\rho$induces a classical probability measure~$\pmeas':2^{\Omega}\rightarrow[0,1]$
on $\Omega$. Let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
be the quantum event corresponding to subspace span by $E$, we can
have
\begin{equation}
\pmeas'\left(E\right)=\mu_{\rho}^{B}\left(P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}\textrm{ .}\label{BornRule.mixed-1}
\end{equation}
By equation (\ref{eq:Radon-Nikodym}), the Radon-Nikodym derivative
of $\pmeas'$ $f:\Omega\rightarrow[0,1]$ is just the diagonal elements
of $\rho$:

\begin{equation}
f\left(\ket{\psi_{j}}\right)=r_{jj}\textrm{ .}\label{eq:quantum-Radon-Nikodym}
\end{equation}

In this sense, the Radon-Nikodym derivative~$f$ is a special case
of the density matrix~$\rho$, and the Radon-Nikodym theorem is a
special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
